---
title: "Pstat 131 Final Project"
author: "Yu Tian"
date: "Spring 2022-04-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      results = 'markup',
                      fig.width = 4,
                      fig.height = 3,
                      fig.align = 'center',
                      message = F,
                      warning = F)

# packages
library(tidyverse)
library(tidymodels)
library(ISLR)
library(ggplot2)
library(corrplot)
library(yardstick)
tidymodels_prefer()
```

## Data Demo

```{r}
# Read the full data set into R using read_csv()
fat_supply_quantity <- read.csv(file = 'Fat_Supply_Quantity_Data.csv')
fat_supply_quantity %>% 
  head()

protein_supply_quantity <- read.csv(file = 'Protein_Supply_Quantity_Data.csv')
protein_supply_quantity %>% 
  head()

food_supply_quantity_kg <- read.csv(file = 'Food_Supply_Quantity_kg_Data.csv')
food_supply_quantity_kg %>% 
  head()

food_supply_kcal <- read.csv(file = 'Food_Supply_kcal_Data.csv')
food_supply_kcal %>% 
  head()

descriptions <- read.csv(file = 'Supply_Food_Data_Descriptions.csv')
descriptions %>% 
  head()
```

I may only use the first four files.

## An overview of your dataset

#### What does it include
?

COVID-19 Healthy Diet Dataset in different counties



#### Where and how will you be obtaining it? Include the link and source
.

https://www.kaggle.com/datasets/mariaren/covid19-healthy-diet-dataset?select=Food_Supply_kcal_Data.csv


#### About how many observations? How many predictors
?

170 observations

about 101 predictors


#### What types of variables will you be working with
?

I will mainly work with the data related with covid-19.


#### Is there any missing data? About how much? Do you have an idea for how to handle it
?

no (temporary)

## An overview of your research question(s)

#### What variable(s) are you interested in predicting? What question(s) are you interested in answering
?

What kind of food is best for avoid infection of covid-19 and helpful for recovery?
What kind of food combinations are good for avoid infection of covid-19 and helpful for recovery?

#### Name your response/outcome variable(s) and briefly describe it/them
.

food_type

#### Will these questions be best answered with a classification or regression approach
?

maybe classification

#### Which predictors do you think will be especially useful
?

percentage of COVID-19 active/death/confirmed/recover cases

#### Is the goal of your model descriptive, predictive, inferential, or a combination? 
Explain.

combination


## Your proposed project timeline
#### When do you plan on having your data set loaded, beginning your exploratory data analysis, etc?
Provide a general timeline for the rest of the quarter.

I have loaded the data set, but they still need to be resort to research

## Any questions or concerns
####Are there any problems or difficult aspects of the project you anticipate?
####Any specific questions you have for me/the instructional team?

the predictors is too many, so choosing a specific direction to research is difficult for me now
